upwell_IDX

### 2020-04-27 upwell_IDX.Rmd
update

wind_daily <- wind_data %>% 
  filter(temp_sites %in% selected_sites) %>%  # Matching the sites to wind temp sites
  dplyr::group_by(temp_sites, date) %>%
  dplyr::summarise(dir_circ = round(mean.circular(circular(dir, units = "degrees", 
                                                           template = 'geographics')),2),
                                    spw_circ = mean.circular(circular(speed, units = "degrees"))) # Direction using the circular function
# save(wind_daily, file = "Data_coast_angle/wind_daily.RData")

# library(openair)
# wind_daily_speed <- timeAverage(wind_data, avg.time = "day")
# # save(wind_daily, file = "Data/wind_daily.RData") 
# #Convert Wind Speed and Wind Direction to u/v Wind Components 
# # Then get the daily average and then convert it back?
# # https://rdrr.io/github/retostauffer/Rfoehnix/man/ddff2uv.html
# # Use with zoo
# 
# library("zoo")
# set.seed(100)
# Sys.setenv("TZ" = "UTC")
# ## Calculate dd/ff
# wind_data <- wind_data %>% 
#   rename(dd = dir,
#          ff = speed)
# 
# uv <- ddff2uv(wind_data)
# #blowing to
```

>>>>

wind_daily <- wind_daily_tested%>%
  dplyr::summarise(dir_circ = round(mean.circular(circular(dir, units = "degrees", 
                                                           template = 'geographics')),2),
                                    spw_circ = mean.circular(circular(speed, units = "degrees"))) # Direction using the circular function
# save(wind_daily, file = "Data_coast_angle/wind_daily.RData")

# library(openair)
# wind_daily_speed <- timeAverage(wind_data, avg.time = "day")

# #Convert Wind Speed and Wind Direction to u/v Wind Components 
# # Then get the daily average and then convert it back?
# # https://rdrr.io/github/retostauffer/Rfoehnix/man/ddff2uv.html
# # Use with zoo
# 
# library("zoo")
# set.seed(100)
# Sys.setenv("TZ" = "UTC")
# ## Calculate dd/ff
# wind_data <- wind_data %>% 
#   rename(dd = dir,
#          ff = speed)
# 
# uv <- ddff2uv(wind_data)
```
